Spatial Reasoning and Statistical Graphics

### 2014-11-18 Paper/Draft1/TestingVisualAptitude.Rnw
edits during the meeting

\comment{Next few steps for the analysis: \\
(3) in terms of why we would use lineups in a test comparison ... lineups give us a way to say 'this is correct' which regular graphics don't. So we should put a spin sentence on at the intro and the back that we are suggesting to use lineups as a tool to not only evaluate individuals (which we can see is possible) but also as a tool to evaluate charts ... which we've done before ... and tie it into the regular testing literature ...\\
\textbf{A few sentences added, still need to tie into the existing literature}\\
(4) I'll take care of the intro to lineups}

@@

>>>>

\comment{Next few steps for the analysis: \\
(3) in terms of why we would use lineups in a test comparison ... lineups give us a way to say 'this is correct' which regular graphics don't. So we should put a spin sentence on at the intro and the back that we are suggesting to use lineups as a tool to not only evaluate individuals (which we can see is possible) but also as a tool to evaluate charts ... which we've done before ... and tie it into the regular testing literature ...\\
\textbf{A few sentences added, still need to tie into the existing literature}\\
(4) I'll take care of the intro to lineups\\
(5) Include lineup results from other studies. For that, we need to compare percent correct attempted data. 
}

@@

\comment{ Just collecting items:
lineups are classification tests, not necessarily visual tests; 
individual tasks are somewhat more related to individual tests, but no overall general trend towards any of the other tests besides figure classification.

mathematical training - could be interesting follow-up study.

amazon turk study - how generalizable are they.

use figure classification for pre-screening without biasing; i.e. as baseline criteria or for exclusion of participants from future amazon turk studies.

}
